Races with hyper3 objects

### 2022-06-26 inst/race3.Rmd
consistent likelihood function

>>>>

## Results for AAAB

```{r,plotaaab,cache=TRUE}
Hab <- function(i,n=4){
  jj <- rep("a",n)
  jj[i] <- "b"
  ordervec2supp3(jj)
}

small <- 1e-5
a <- seq(from=small,to=1-small,len=100)
plot(0:1,c(0,1),type="n",xlab="p[a]",ylab="likelihood")
dop <- function(w, ...){
  Hjj <- Hab(w)
  y <- sapply(a,function(p){loglik(c(a=p,b=1-p),Hjj,log=FALSE)})
  points(a,y/max(y),type="l",...)
}
dop(1,col="black")
dop(2,col="red")
dop(3,col="blue")
dop(4,col="green")

```
